BPMN Analyzer 2.0: Instantaneous, Comprehensible, and Fixable Anomaly Detection for BPMN Models

### 2024-07-04 main.tex
Next section

@@

% Extended version on GitHub and then on Arxiv once submitted

% An introduction section, which, among others, should highlight the significance of the tool or resource to the BPM field;
\section{Introduction}

@@

% Must have section according to the description
% A section discussing the innovations of the tool or resource to the BPM community and its main characteristics or features
\section{Innovations} \label{sec:innovations} % Main tool description and showing the innovations
Three main innovations of the tool:
% Instantaneous
% Comprehensible
% Fixable

% They also want this section
\section{Maturity of the tool} \label{sec:maturity}
% Discuss/highlight the implementation: Test cases, static analysis etc. industrial standard! ;)
% Scalability tests (instantaneous) --> Generated models are public including our tool for future direct comparisons
Improves upon our previous BPMN Analyzer tool~\cite{krauterFormalizationAnalysisBPMN2023}.

@@

% TODO: Update DOI link to fit the extended version on arxiv
% Extended version: \cite{krauterInstantaneousComprehensibleFixable2024}

>>>>

% TODO: Soundness vs anomaly detection? Maybe use soundness and say later that in the UI, it's not called soundness!

@@

\section{Introduction}

@@

% Must have section according to the description
% A section discussing the innovations of the tool or resource to the BPM community and its main characteristics or features
\section{Innovations} \label{sec:innovations} % Main tool description and showing the innovations
The BPMN Analyzer has three main innovations: \textbf{instantaneous}, \textbf{comprehensible}, and \textbf{fixable} anomaly detection.
In this section, we will present the innovations, and more details can be found in our extended paper \cite{krauterInstantaneousComprehensibleFixable2024}.
% Instantaneous
% Comprehensible
% Fixable

% They also want this section
\section{Maturity of the tool} \label{sec:maturity}
% Discuss/highlight the implementation: Test cases, static analysis, etc., industrial standard! ;)
% Scalability tests (instantaneous) --> Generated models are public, including our tool for future direct comparisons
The BPMN Analyzer is our newest tool, incorporating many findings from our previous work \cite{krauterFormalizationAnalysisBPMN2023} while focusing on instantaneous and understandable anomaly detection.

@@

% TODO: Update the DOI link to fit the extended version on arxiv
% Extended version: \cite{krauterInstantaneousComprehensibleFixable2024}
